What is MaxEnt?

### 2015-06-11 ms.tex
Boldsymbol

\newcommand{\hyperparams}{\boldsymbol{\alpha}}
\newcommand{\xx}{\mathbf{x}}

@@

Relative entropy
\begin{eqnarray}
H(\mathbf{p}; \mathbf{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}

@@

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
knowledge about a vector of quantities $\mathbf{x}$. Consider some
function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $f$, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:expectations}.

@@

\begin{eqnarray}
q(\mathbf{x}) \propto
\left\{
\begin{array}{lr}
1, & \forall x_i > 0\\
0, & \textnormal{otherwise}.
\end{array}
\right.
\end{eqnarray}

>>>>

\newcommand{\hyperparams}{\boldsymbol{\alpha}}
\newcommand{\xx}{\boldsymbol{x}}

@@

Relative entropy
\begin{eqnarray}
H(\boldsymbol{p}; \boldsymbol{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}

@@

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\boldsymbol{x})$ describing a state of
knowledge about a vector of quantities $\boldsymbol{x}$. Consider some
function of the unknowns, such as $F=f(\boldsymbol{x}) = \sum_{i=1}^N x_i$.
If the value of $F$ is known, then our distribution for $\boldsymbol{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $F$, then our distribution for $\boldsymbol{x}$ can
be updated as in Section~\ref{sec:expectations}.

@@

\begin{eqnarray}
q(\boldsymbol{x}) \propto
\left\{
\begin{array}{lr}
1, & \forall x_i > 0\\
0, & \textnormal{otherwise}.
\end{array}
\right.
\end{eqnarray}

For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:

\begin{eqnarray}
p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}
\end{eqnarray}
